Fourmile Calibrations

### 2022-12-12 calibration_output.Rmd
finished getting kge values by reach

@@

## Hydrograph

@@

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s')

@@

## Overall KGE

@@

## Model run KGE by water year

@@

## Model run KGE plots by water year

@@

>>>>

### Parameters for each calibration run

@@

### Density plots: station vs. grid

```{r density plots, echo = F}

mean_params <- params %>%
  group_by(param, input_data) %>%
  summarize(mean = mean(value))

plotdens_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = value,
               fill = input_data, 
               color = input_data)) + 
    geom_density(alpha=0.4) +
    geom_vline(data=filter(mean_params, param == param_name), 
               aes(xintercept=mean, color=input_data),
             linetype="dashed", size=0.75) +
    ggtitle(param_name) +
    theme_bw()
}

lapply(name, plotdens_params)

## Outlet results

### Hydrograph (outlet)

@@

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(WY = as.factor(calcWaterYear(date)))

@@

### Hydrograph by WY

```{r wy hydrographs, echo = F}

plotq_wy <- function(wateryear) {
  {flow_pivot %>%
    filter(WY == wateryear) %>%
    ggplot(aes(x = date,
               y = q_m3s,
               color = cal_run)) + 
    geom_line() + 
    ggtitle(wateryear) +
    theme_bw()} %>%
    ggplotly()

}

name <- levels(flow_pivot$WY)

try <- lapply(name, plotq_wy)

htmltools::tagList(try)

### Overall KGE (outlet)

@@

### Model run KGE by water year (outlet)

@@

### Model run KGE plots by water year

@@

## Reach results

### Hydrograph by reach

```{r reach hydrographs, echo = F}

reach <- read_csv('reach_all.csv') %>%
  mutate(reach = as.factor(reach)) %>%
  pivot_longer(!c(date, reach, WY), names_to = 'cal', values_to = 'q_cms')

plotq_reach <- function(reach_name) {
  {reach %>%
    filter(reach == reach_name) %>%
    ggplot(aes(x = date,
               y = q_cms,
               color = cal)) + 
    geom_line() + 
    ggtitle(reach_name) +
    theme_bw()} %>%
    ggplotly()

}

name <- levels(reach$reach)

try2 <- lapply(name, plotq_reach)

htmltools::tagList(try2)

### Overall KGE by reach

```{r reach kge, echo = F}

reach_pivot <- reach %>%
  pivot_wider(names_from = 'cal', values_from = 'q_cms') %>%
  mutate(WY = as.factor(calcWaterYear(date)))

reach_kge_all <- reach_pivot %>%
  group_by(reach) %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

reach_kge_all <- reach_kge_all %>%
  pivot_longer(!reach, names_to = 'cal_runs', values_to = 'KGE') %>%
  pivot_wider(names_from = 'reach', values_from = 'KGE')

kable(reach_kge_all) %>%
  kable_styling(full_width = F)

obs_count <- reach_pivot %>%
  select(obs, reach) %>%
  drop_na() %>%
  group_by(reach) %>%
  summarize(count_obs = n())

kable(obs_count, caption = 'Streamflow observation count') %>%
  kable_styling(full_width = F)
